Inferring community characteristics in labelled networks

### 2021-05-14 nips/submission.tex
More twitch work

		\FOR{$t \in \{0, 1 \dots T_b - 1\}$}
			\STATE $b' \gets \sim q_b(b^{(t)}, b' | A)$
			\STATE $\log \alpha_b \gets \log \alpha_b(b^{(t)}, b' | A)$
			\STATE $u \gets \sim \textrm{Unif}(0,1)$
			\IF{$\log u < \log \alpha_b$}
				\STATE $b^{(t+1)} \gets b'$
			\ELSE
				\STATE $b^{(t+1)} \gets b^{(t)}$
			\ENDIF
		\ENDFOR

@@

		\FOR{$t \in \{0, 1 \dots T_\theta - 1\}$}
		\STATE $\theta' \gets \sim q_\theta(\theta^{(t)}, \theta' | X, \hat{Y})$
		\STATE $\log \alpha_\theta \gets \log \alpha_\theta(\theta^{(t)}, \theta' | A, \hat{Y})$
		\STATE $u \gets \sim \textrm{Unif}(0,1)$
		\IF{$\log u < \log \alpha_\theta$}
		\STATE $\theta^{(t+1)} \gets \theta'$
		\ELSE
		\STATE $\theta^{(t+1)} \gets \theta^{(t)}$
		\ENDIF
		\ENDFOR

@@

>>>>

		\FOR{$t \in \{0, 1 \dots T_b - 1\}$}
			\STATE $b' \gets \sim q_b(b^{(t)}, b' | A)$
			\STATE $\log \alpha_b \gets \log \alpha_b(b^{(t)}, b' | A)$
			\STATE $\eta \gets \sim \textrm{Unif}(0,1)$
			\IF{$\log \eta < \log \alpha_b$}
				\STATE $b^{(t+1)} \gets b'$
			\ELSE
				\STATE $b^{(t+1)} \gets b^{(t)}$
			\ENDIF
		\ENDFOR

@@

		\FOR{$t \in \{0, 1 \dots T_\theta - 1\}$}
		\STATE $\xi \gets \sim \Gaussian(0, I)$
		\STATE $\theta' \gets \theta^{(t)} - h_t \nabla U(\theta^{(t)} | X, \hat{Y}) + \sqrt{2h_t} \cdot \xi$
		\STATE $\log \alpha_\theta \gets \log \alpha_\theta(\theta^{(t)}, \theta' | A, \hat{Y})$
		\STATE $\eta \gets \sim \textrm{Unif}(0,1)$
		\IF{$\log \eta < \log \alpha_\theta$}
		\STATE $\theta^{(t+1)} \gets \theta'$
		\ELSE
		\STATE $\theta^{(t+1)} \gets \theta^{(t)}$
		\ENDIF
		\ENDFOR

@@

\subsection{Choosing the MALA step-size}
\label{appdx:step-size}

For sampling from the $\theta$-chain of the block membership generator parameters, we employed the Metropolis Adjusted Langevin Algorithm (MALA). At iteration $t$, the proposed sample is generated by:
%
\begin{equation}
	\theta' = \theta^{(t)} - h_t \nabla U(\theta^{(t)}) + \sqrt{2h_t} \cdot \xi
\end{equation}
%
There are two competing objectives when choosing the step-size $h_t$. On the one hand, we want the step-size to be large so that we arrive at a high density region quickly. However, too large a step-size will lead to a lower acceptance ratio and thus inefficient sampling. A solution to this problem would be to slowly decrease the step-size with $t$ - often called simulated annealing. Therefore, we still have a short burn-in time but will not bounce around the mode for large $t$. As well as the trivial constraint for $h_t$ to be strictly positive and we introduce two further constraints as outlined by \citet{Bayesian-SGLD}:
%
\begin{equation}
	\sum_{t=1}^{\infty} h_t = \infty \qquad \textrm{and} \qquad
	\sum_{t=1}^{\infty} h_t^2 < \infty
	\label{eqn:h-constraints}
\end{equation}
%
The first constraint ensures that we have cover sufficient distance to arrive at any arbitrary point in our domain, no matter the starting point. The second constraint ensures that once we converge to the mode rather than simply bouncing around it. \citet{Bayesian-SGLD} propose the following form for a polynomially decaying step-size which we adopt:
%
\begin{equation}
	h_t = a(b + t)^{-\gamma}
\end{equation}
%
Where $a, b, \gamma$ are hyper-parameters to be chosen. We require $a,b > 0$ and $\gamma \in (0.5, 1]$ to satisfy equation \ref{eqn:h-constraints}. We find empirically that $a=250, b=1000, \gamma=0.8$ yield good burn-in times for our MALA implementations.
